The Legacy of the European Post-Master in Urbanism at TU Delft: A Text Mining Approach

### 2023-07-05 analysis/paper/paper.qmd
Add code chunk labels and update layout

```{r topic-model-lda}
emu_theses_topics <- get_topics(emu_theses_words)

emu_theses_topics_terms <- tidy(emu_theses_topics, matrix = "beta")
emu_theses_topics_documents <- tidy(emu_theses_topics, matrix = "gamma")

@@

# TODO can this be generalised to more than two topics?
# beta_spread <- emu_theses_topics_terms |> 
beta_spread <- emu_theses_topics |> 
  mutate(topic = paste0("topic", topic)) |> 
  spread(topic, beta) |> 
  filter(topic1 > 0.001, topic2 > .001) |> 
  mutate(log_ratio = log2(topic2/topic1))

@@

```{r}
# Which are the top n most frequently used words in each thesis?
get_top_words_per_document(data = emu_theses_words, top_n = 3)
```

```{r}
# Which are the top n most frequently used words in all theses?
n = 20

# TODO add topic to fill aesthetic
get_top_words_per_corpus(data = emu_theses_words |> 
                           mutate(word = textstem::lemmatize_words(emu_theses_words$word)), top_n = n) |> 
  ggplot(aes(reorder(word, n), n)) +
  geom_col(fill = "orange") +
  geom_text(aes(label = n), size = 2, hjust = 1.1) +
  coord_flip() +
  xlab("Word") +
  ylab("Frequency") +
  labs(title = paste0("Top ", n, " most used words in the corpus of theses"))
  theme_minimal() +
  theme(panel.grid = element_blank())

@@

```{r tf-idf}
## Calculate tf-idf statistic
emu_theses_tf_idf <- emu_theses_words |> 
  get_tf_idf(title_col = "title", word_col = "word")

## Get top n words most specific to each thesis 
emu_theses_tf_idf |> 
  group_by(title) |> 
  top_n(5, tf_idf) |> 
  arrange(desc(tf_idf), .by_group = TRUE)
```

@@

```{r word-embeddings}

@@

```{r word-embeddings}

>>>>

```{r topic-model-lda}

@@

# TODO can this be generalised to more than two topics?
beta_spread <- emu_theses_topics |> 
  mutate(topic = paste0("topic", topic)) |> 
  spread(topic, beta) |> 
  filter(topic1 > 0.001, topic2 > .001) |> 
  mutate(log_ratio = log2(topic2/topic1))

@@

```{r top-words-document}
# Which are the top n most frequently used words in each thesis?
get_top_words_per_document(data = emu_theses_words, top_n = 3)
```

```{r top-words-corpus}
# Which are the top n most frequently used words in all theses?
# TODO add `topic` to `fill` aesthetic
get_top_words_per_corpus(data = emu_theses_words, top_n = 50) |>
  ggplot(aes(reorder(word, n), n)) +
  geom_col(fill = "orange") +
  geom_text(aes(label = n), size = 2, hjust = 1.1) +
  coord_flip() +
  xlab("Word") +
  ylab("Frequency") +
  labs(title = paste0("Top ", n, " most used words in the corpus of theses")) +
  theme_minimal() +
  theme(panel.grid = element_blank())
```

@@

```{r tf-idf}

## Calculate tf-idf statistic
emu_theses_tf_idf <- emu_theses_words |> 
  get_tf_idf(title_col = "title", word_col = "word")

## Get top n words most specific to each thesis 
emu_theses_tf_idf |> 
  group_by(title) |> 
  top_n(5, tf_idf) |> 
  arrange(desc(tf_idf), .by_group = TRUE)

@@

```{r word-embeddings-vis}

@@

```{r doc-embeddings}
